\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-21 icse/eval.tex
Re-order negative tests

\begin{table}
  \centering
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Negative tests & 2,280\\\hdashline
    Inessential built-in objects tests & \inred{XXXX}\\\hdashline
    Tests for not yet modeled semantics & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
  \caption{The results of tests in the test262 for ECMAScript 2020.}
  \label{table:test262}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Negative tests & 2,628\\\hdashline
    Non-strict tests & 1,064\\\hdashline
    Module tests& 642 \\\hdashline
    Inessential built-in objects tests & \inred{XXXX}\\\hdashline
    Tests for not yet modeled semantics & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
  \caption{The results of tests in the test262 for ECMAScript 2020.}
  \label{table:test262}
\end{table}
